Model

### 2019-04-17 stats/model.Rmd
first pass model inferring semantic strength
model debugging; speakerOptimality not defined

var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)

@@

    var conditionData = _.filter(data, {condition: cndtn})

    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})

@@

      var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)

      observe(modelPredictions, row.correct)

@@

    return extend([
      {int: sem_int, slope: sem_slope, familiar: cndtn}
    ])

@@

params

}
'
```

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 5000, burn = 2000, verbose = T)
)

>>>>

var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality, sem_knowledge)

@@

    // display(data.slice(0, 4))
    // display(cndtn)
    var conditionData = _.filter(data, {familiar: cndtn})

    var sem_slope = uniformDrift({a: -5, b: 5, width: 0.2})
    var sem_int = uniformDrift({a: 0, b: 5, width: 0.2})    
    // display(conditionData)

@@

      var modelPredictions = pragmaticListener({label: "novel_word"}, priorProbs, speakerOptimality,sem_knowledge)
      // display(row.correct)
      observe(modelPredictions, row.correct)

@@

    return {int: sem_int, slope: sem_slope, familiar: cndtn}

@@

params
}
'
```

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "MCMC", samples = 5, burn = 1, verbose = T)
)
